Measuring individual differences in the understanding of gaze cues

### 2022-02-21 paper/manuscript.Rmd
add participant sections

@@

The web-app was programmed in JavaScript (ECMAScript 2015, i.e., ES6), HTML5, CSS and PHP. 
For the web-app development, we chose the zero configuration bundler Parcel. It enables a live server for debugging, makes imports easy, and minifies scripts in order to save data storage.
For the design of the landing pages, the CSS library Material Components Web (TODO: insert citation) was used. 
For stimulus presentation, a scalable vector graphic (SVG) composition was parsed. This way, the composition scales according to the user's view port without loss of quality, while keeping the aspect ratio and relative object positions constant. 
Furthermore, SVGs allow us to define all composite parts of the scene (e.g., pupil of the agent) individually. This is needed for precisely calculating exact pupil and target locations and sizes. Additionally, it makes it easy to adjust the stimuli and, for example, add another agent to the scene.
The GreenSock Animation Platform (GSAP; TODO: insert citation) library was used to animate the movement of single SVG elements.

@@

## Data processing
- workflow server to R, converting coordinate systems
We used `r cite_r("r-references.bib")` for all our analyses.

# Does the balloon finding task induce variation?
## Participants: kiga & prolific vali
## Procedure
## Results
- for hedge & box
- sanity check: developmental trajectory
- remote testing: online child sample as side note

# Can we capture variation reliably?
## Participants: religa kiga & prolific reli
## Procedure: 14 ± 3 days
- what is different compared to variation? nr of trials, fixed order
## Results
- internal consistency
- test-retest

# Exploring the external validity of our task
## Participants: subset kiga & relikiga that filled out questionnaires
## Results
- peer exposure (hedge & box combined?)

@@

50 adults participated in the study. One additional subject returned their submission, i.e., decided to leave the study early or withdrew their submission after study completion. Data collection took place in May 2021.

Participants were compensated with £1.25 for completing the study. We estimated an average completion time of 6 minutes, resulting in an estimated hourly rate of £10.00. In average, participants took 05:56min to complete the study.

Participants were required to complete the study on a tablet or desktop.Participation on mobile devices was disabled since the display would be too small and would harm click precision. It was indicated that the study required audio sound.

@@

After clicking the study title, participants were directed to our online study website.
...

### Study 2 - Validation box version
As in study 1, we recruited participants on *Prolific*, and employed the same methodology. However, this time we focussed on validating the box version of the task in an adult sample. Participants were presented with eight boxes in which the target could land.

50 adults participated in the study. One additional subject returned their submission, i.e., decided to leave the study early or withdrew their submission after study completion. Data collection took place in June 2021.

Participants were compensated with £1.00 for completing the study. We estimated an average completion time of 6 minutes, resulting in an estimated hourly rate of £10.00. In average, participants took 04:43min to complete the study.

@@

## Child sample
```{r}
library(tidyverse)
testtrials <- readRDS(file = "../data/gafo-testtrials.rds") %>% 
  # determine order of factors
  mutate(
    targetPosition = factor(targetPosition, levels = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "box1", "box2", "box3", "box4", "box5")), 
    studyversion = factor(studyversion, levels = c("hedge", "box")), 
    datacollection = factor(datacollection, levels = c("in-person - supervised", "remote - unsupervised")),
    sample = factor(sample, levels = c("kids", "adults")), 
    studytype = factor(studytype, levels = c("vali", "vali2", "reli"))
  )

kids_vali <- testtrials %>% 
  filter(ageInYears < 6 & studytype == "vali")

kids_vali_inperson_sample <- kids_vali %>%
  filter(datacollection == "in-person - supervised") %>% 
  group_by(ageInYears) %>%
  summarise(
    nTotal = n_distinct(subjID), 
    meanAgeInMonths = mean(ageInMonths, na.rm = T) %>% round(2),
    sdAgeInMonths = sd(ageInMonths, na.rm = T) %>% round(2),
    minAgeInMonths = min(ageInMonths, na.rm = T),
    maxAgeInMonths = max(ageInMonths, na.rm = T),
  )

# kids_vali %>% 
#   filter(datacollection == "in-person - supervised") %>% 
#   group_by(ageInYears, gender) %>% 
#   summarise(
#     n = length(unique(subjID))
#   )
```

### Study 1 - Validation Remote and in-person
The validation of our task in a in-person and remote child sample can be found here: https://osf.io/snju6. 
We chose to have at least 20 data points per cell (i.e. unique combination of data collection mode, study version, and age-group). Across the two data collection modes, a total of `r kids_vali %>% select(subjID) %>% n_distinct()` children participated. Participants received a small gift as thank you for their participation in the study.

@@

Our in-person supervised testing sample involved `r kids_vali %>% filter(datacollection == "in-person - supervised") %>% select(subjID) %>% n_distinct()` children, including `r kids_vali_inperson_sample %>% filter(ageInYears == "3") %>%  select(nTotal)` 3-year-olds (mean = `r kids_vali_inperson_sample %>% filter(ageInYears == "3") %>%  select(meanAgeInMonths)` months, SD = `r kids_vali_inperson_sample %>% filter(ageInYears == "3") %>%  select(sdAgeInMonths)`, range = `r kids_vali_inperson_sample %>% filter(ageInYears == "3") %>%  select(minAgeInMonths)` - `r kids_vali_inperson_sample %>% filter(ageInYears == "3") %>%  select(maxAgeInMonths)`, 22 girls), `r kids_vali_inperson_sample %>% filter(ageInYears == "4") %>%  select(nTotal)` 4-year-olds (mean = `r kids_vali_inperson_sample %>% filter(ageInYears == "4") %>%  select(meanAgeInMonths)` months, SD = `r kids_vali_inperson_sample %>% filter(ageInYears == "4") %>%  select(sdAgeInMonths)`, range = `r kids_vali_inperson_sample %>% filter(ageInYears == "4") %>%  select(minAgeInMonths)` - `r kids_vali_inperson_sample %>% filter(ageInYears == "4") %>%  select(maxAgeInMonths)`, 19 girls), and `r kids_vali_inperson_sample %>% filter(ageInYears == "5") %>%  select(nTotal)` 5-year-olds (mean = `r kids_vali_inperson_sample %>% filter(ageInYears == "5") %>%  select(meanAgeInMonths)` months, SD = `r kids_vali_inperson_sample %>% filter(ageInYears == "5") %>%  select(sdAgeInMonths)`, range = `r kids_vali_inperson_sample %>% filter(ageInYears == "5") %>%  select(minAgeInMonths)` - `r kids_vali_inperson_sample %>% filter(ageInYears == "5") %>%  select(maxAgeInMonths)`, 22 girls).

```{r}
# test papajas apa tables
apa_table(kids_vali_inperson_sample, 
          caption = "Child sample", 
          note = "in-person supervised testing", 
          # align = c("l", "r", "c"), 
          escape = FALSE, 
          row.names = TRUE, 
          placement = "h")
```

>>>>

```{r load_data}
library(tidyverse)
testtrials <- readRDS(file = "../data/gafo-testtrials.rds") %>% 
  # determine order of factors
  mutate(
    targetPosition = factor(targetPosition, levels = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "box1", "box2", "box3", "box4", "box5")), 
    studyversion = factor(studyversion, levels = c("hedge", "box")), 
    datacollection = factor(datacollection, levels = c("in-person - supervised", "remote - unsupervised")),
    sample = factor(sample, levels = c("kids", "adults")), 
    studytype = factor(studytype, levels = c("vali", "vali2", "reli"))
  )
```

@@

The web-app was programmed in JavaScript (ECMAScript 2015, i.e., ES6), HTML5, CSS and PHP. 
For the web-app development, we chose the zero configuration bundler Parcel. It enables a live server for debugging, makes imports easy, and minifies scripts in order to save data storage.
For the design of the landing pages, the CSS library Material Components Web (TODO: insert citation) was used. 
For stimulus presentation, a scalable vector graphic (SVG) composition was parsed. This way, the composition scales according to the user's view port without loss of quality, while keeping the aspect ratio and relative object positions constant. 
Furthermore, SVGs allow us to define all composite parts of the scene (e.g., pupil of the agent) individually. This is needed for precisely calculating exact pupil and target locations and sizes. Additionally, it makes it easy to adjust the stimuli and, for example, add another agent to the scene.
The GreenSock Animation Platform (GSAP; TODO: insert citation) library was used to animate the movement of single SVG elements. 
We use URL parameters to capture the participant's ID, language and study version.

@@

## Data processing
- workflow server to R, converting coordinate systems
We used `r cite_r("r-references.bib")` for all our analyses.
For child samples, we uploaded safety copies of the already collected responses after the fourth test trial. In cases where children want to stop participation earlier, no responses get lost. All test trials without voice over description are included in our analyses.

# Does the balloon finding task induce variation?
```{r vali_sample}
vali <- testtrials %>% 
  filter(studytype == "vali" & (ageInYears < 6 | ageInYears == 18))

vali_kids <- vali %>%
  filter(ageInYears < 6) %>% 
  group_by(datacollection, ageInYears) %>%
  summarise(
    nTotal = n_distinct(subjID), 
    meanAgeInMonths = mean(ageInMonths, na.rm = T) %>% round(2),
    sdAgeInMonths = sd(ageInMonths, na.rm = T) %>% round(2),
    minAgeInMonths = min(ageInMonths, na.rm = T),
    maxAgeInMonths = max(ageInMonths, na.rm = T),
  )

vali_kids_gender <- vali %>% 
  filter(ageInYears < 6) %>% 
  group_by(datacollection, ageInYears) %>%
  filter(gender == "f") %>% 
  summarise(
    nFemales = length(unique(subjID))
  )

vali_kids <- vali_kids %>% 
  left_join(vali_kids_gender, by = c("datacollection", "ageInYears"))

vali_adults <- vali %>%
  filter(ageInYears == 18) %>% 
  summarise(
    nTotal = n_distinct(subjID), 
    meanAge = mean(age, na.rm = T) %>% round(2),
    sdAge = sd(age, na.rm = T) %>% round(2),
    minAge = min(age, na.rm = T),
    maxAge = max(age, na.rm = T),
  )

vali_adults_gender <- vali %>% 
  filter(ageInYears == 18 & gender == "f") %>% 
  summarise(
    nFemales = length(unique(subjID))
  )

vali_adults <- vali_adults %>% 
  full_join(vali_adults_gender, by = character())
```
## Participants
Our first aim was to assess whether our balloon finding task induces variation in a child and adult sample. The pre-registrations can be found here: https://osf.io/snju6 (child sample) and here: https://osf.io/r3bhn (adult sample). Participants were equally distributed across the two study versions.

For our child sample, we went to kindergartens in Leipzig and surroundings that cooperate with the Max Planck Institute for Evolutionary Anthropology. Children in our sample grow up in an industrialized, urban Central-European context. Information on socioeconomic status was not formally recorded, although the majority of families come from mixed, mainly mid to high socioeconomic backgrounds with high levels of parental education. 
The child sample consisted of 
`r sum(vali_kids$nTotal[vali_kids$datacollection == "in-person - supervised"])` children, including 
`r sum(vali_kids$nTotal[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "3"])` 3-year-olds 
(mean = `r sum(vali_kids$meanAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "3"])` months, 
SD = `r sum(vali_kids$sdAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "3"])`, 
range = `r sum(vali_kids$minAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "3"])`
- `r sum(vali_kids$maxAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "3"])`, 
`r sum(vali_kids$nFemales[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "3"])` girls),
`r sum(vali_kids$nTotal[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "4"])` 4-year-olds 
(mean = `r sum(vali_kids$meanAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "4"])` months, 
SD = `r sum(vali_kids$sdAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "4"])`, 
range = `r sum(vali_kids$minAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "4"])`
- `r sum(vali_kids$maxAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "4"])`, 
`r sum(vali_kids$nFemales[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "4"])` girls),
and `r sum(vali_kids$nTotal[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "5"])` 5-year-olds 
(mean = `r sum(vali_kids$meanAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "5"])` months, 
SD = `r sum(vali_kids$sdAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "5"])`, 
range = `r sum(vali_kids$minAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "5"])`
- `r sum(vali_kids$maxAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "5"])`, 
`r sum(vali_kids$nFemales[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "5"])` girls). 
Children received a small thank-you gift for their participation in the study.

In addition, we recruited adult participants by advertising the study on *Prolific*. *Prolific* is an online participant recruitment service from the University of Oxford with a predominantly European and US-american subject pool. Participants consisted of `r vali_adults$nTotal` English-speakers with an average age of `r vali_adults$meanAge` years (SD = `r vali_adults$sdAge`, range = `r vali_adults$minAge` - `r vali_adults$maxAge`, `r vali_adults$nFemales` females). 
For completing the study, subjects were payed above the fixed minimum wage (in average £10.00 per hour). *Prolific* distributed our study link to potential participants, while the hosting of the online study was done by local servers in the Max Planck Institute for Evolutionary Anthropology, Leipzig, Germany.

## Procedure
All participants received 15 test trials that were displayed as described above. In the box version, we decided to adjust the task difficulty according to the participant's age: children were presented with five boxes while adults were presented with eight boxes as possible hiding location of the target.

## Results
- for hedge & box
- sanity check: developmental trajectory
- remote testing: online child sample as side note

To assess whether we would gain similar results in a remote, unsupervised testing context with children, we recruited an additional online sample of `r sum(vali_kids$nTotal[vali_kids$datacollection == "remote - unsupervised"])` children, including 
`r sum(vali_kids$nTotal[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "3"])` 3-year-olds 
(mean = `r sum(vali_kids$meanAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "3"])` months, 
SD = `r sum(vali_kids$sdAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "3"])`, 
range = `r sum(vali_kids$minAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "3"])`
- `r sum(vali_kids$maxAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "3"])`, 
`r sum(vali_kids$nFemales[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "3"])` girls),
`r sum(vali_kids$nTotal[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "4"])` 4-year-olds 
(mean = `r sum(vali_kids$meanAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "4"])` months, 
SD = `r sum(vali_kids$sdAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "4"])`, 
range = `r sum(vali_kids$minAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "4"])`
- `r sum(vali_kids$maxAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "4"])`, 
`r sum(vali_kids$nFemales[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "4"])` girls),
and `r sum(vali_kids$nTotal[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "5"])` 5-year-olds 
(mean = `r sum(vali_kids$meanAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "5"])` months, 
SD = `r sum(vali_kids$sdAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "5"])`, 
range = `r sum(vali_kids$minAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "5"])`
- `r sum(vali_kids$maxAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "5"])`, 
`r sum(vali_kids$nFemales[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "5"])` girls). 
Families were recruited on a voluntary basis via email from the institute internal database. 
In the beginning of the online study, families were invited to enter "our virtual institute" and were welcomed by an introductory video of the study leader, shortly describing the research background and further procedure. Then, caregivers were informed about data security and were asked for their informed consent. They were asked to enable the sound and seat their child centrally in front of their device. Subsequently, a brief demographic questionnaire was displayed, asking for (1) the total number of household members, (2) the number of children, (3) age of the other children, (4) whether the child was in day care, and if yes, (5) since when and (6) for how long on an average day. Before the study started, families were instructed how to setup their webcam and enable the recording permissions. Study participation was video recorded whenever possible in order to ensure that the answers were generated by the children themselves. 
After completion, families received a little crafting / coloring sheet as a small thank-you gift.
Depending on the participant's device, the website automatically presented the hedge or box version of the study. For families that used a tablet with touchscreen, the hedge version was shown. Here, children could directly click on the touchscreen themselves to indicate where the target is. For families that used a computer without touchscreen, the website presented the box version of the task. We assumed that younger children in our sample would not be acquainted with the usage of a computer mouse. Therefore, we asked children to point to the screen. Caregivers were then asked to act as the "digital finger" of their children and click on the indicated box.

# Can we capture variation reliably?
```{r reli_sample}
reli <- testtrials %>% 
  filter(studytype == "reli" & (ageInYears < 6 | ageInYears == 18) & completedReli)

reli_kids <- reli %>%
  filter(ageInYears < 6) %>% 
  group_by(datacollection, ageInYears) %>%
  summarise(
    nTotal = n_distinct(subjID), 
    meanAgeInMonths = mean(ageInMonths, na.rm = T) %>% round(2),
    sdAgeInMonths = sd(ageInMonths, na.rm = T) %>% round(2),
    minAgeInMonths = min(ageInMonths, na.rm = T),
    maxAgeInMonths = max(ageInMonths, na.rm = T),
  )

reli_kids_gender <- reli %>% 
  filter(ageInYears < 6) %>% 
  group_by(datacollection, ageInYears) %>%
  filter(gender == "f") %>% 
  summarise(
    nFemales = length(unique(subjID))
  )

reli_kids <- reli_kids %>% 
  left_join(reli_kids_gender, by = c("datacollection", "ageInYears"))

reli_adults <- reli %>%
  filter(ageInYears == 18) %>% 
  summarise(
    nTotal = n_distinct(subjID), 
    meanAge = mean(age, na.rm = T) %>% round(2),
    sdAge = sd(age, na.rm = T) %>% round(2),
    minAge = min(age, na.rm = T),
    maxAge = max(age, na.rm = T),
  )

reli_adults_gender <- reli %>% 
  filter(ageInYears == 18 & gender == "f") %>% 
  summarise(
    nFemales = length(unique(subjID))
  )

reli_adults <- reli_adults %>% 
  full_join(reli_adults_gender, by = character())
```
## Participants
Our second aim was to assess whether the variation that we captured with our balloon finding task is reliable. The pre-registrations can be found here: https://osf.io/xqm73 (child sample) and here: https://osf.io/nu62m (adult sample).

For our child sample, we again went to kindergartens in Leipzig and surroundings.
The child sample consisted of 
`r sum(reli_kids$nTotal[reli_kids$datacollection == "in-person - supervised"])` children, including 
`r sum(reli_kids$nTotal[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "3"])` 3-year-olds 
(mean = `r sum(reli_kids$meanAgeInMonths[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "3"])` months, 
SD = `r sum(reli_kids$sdAgeInMonths[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "3"])`, 
range = `r sum(reli_kids$minAgeInMonths[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "3"])`
- `r sum(reli_kids$maxAgeInMonths[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "3"])`, 
`r sum(reli_kids$nFemales[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "3"])` girls),
`r sum(reli_kids$nTotal[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "4"])` 4-year-olds 
(mean = `r sum(reli_kids$meanAgeInMonths[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "4"])` months, 
SD = `r sum(reli_kids$sdAgeInMonths[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "4"])`, 
range = `r sum(reli_kids$minAgeInMonths[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "4"])`
- `r sum(reli_kids$maxAgeInMonths[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "4"])`, 
`r sum(reli_kids$nFemales[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "4"])` girls),
and `r sum(reli_kids$nTotal[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "5"])` 5-year-olds 
(mean = `r sum(reli_kids$meanAgeInMonths[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "5"])` months, 
SD = `r sum(reli_kids$sdAgeInMonths[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "5"])`, 
range = `r sum(reli_kids$minAgeInMonths[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "5"])`
- `r sum(reli_kids$maxAgeInMonths[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "5"])`, 
`r sum(reli_kids$nFemales[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "5"])` girls).

The adult sample was again recruited over *Prolific* and consisted of `r reli_adults$nTotal` English-speakers with an average age of `r reli_adults$meanAge` years (SD = `r reli_adults$sdAge`, range = `r reli_adults$minAge` - `r reli_adults$maxAge`, `r reli_adults$nFemales` females).

## Procedure
The procedure was as in the first study, with the following differences. Participants completed the study twice, with a delay of 14 ± 3 days. 
The target locations as well as the succession of animals and target colors was randomized once. Each participant then received this fixed randomized order of target location, animal, and target color. 
The child sample received 15 test trials. In the hedge version, each bin occurred once, making up ten of the test trials. For the remaining five test trials, we repeated one out of two adjacent bins (i.e., randomly chose between bin 1 & 2, bin 3 & 4, etc). In the box version, we ensured that each of the five boxes occurred exactly three times. For the remaining training trials, we repeated a fixed order of four random bins/boxes.
Adults in the hedge version received 30 test trials, each of the ten bin occurring exactly three times. Adults in the box version received 32 test trials with each of the eight boxes occurring exactly four times.

## Results
- internal consistency
- test-retest

# Exploring the external validity of our task
```{r peerexposure_sample}
pe <- testtrials %>% 
  filter(ageInYears < 6) %>% 
  select(datacollection, studyversion, subjID, gender, trialNr, ageInMonths, ageInYears, correctBox, childcareAge, childcareHours, householdTotal, siblingsNr, siblingsChildAged, siblingsVarietyScoreP, siblingsVarietyScoreW, targetPosition, targetCentralityX) %>% 
  # so that all models run with same nr of subjects
  drop_na()

pe_sample <- pe %>%
  group_by(ageInYears) %>%
  summarise(
    nTotal = n_distinct(subjID), 
    meanAgeInMonths = mean(ageInMonths, na.rm = T) %>% round(2),
    sdAgeInMonths = sd(ageInMonths, na.rm = T) %>% round(2),
    minAgeInMonths = min(ageInMonths, na.rm = T),
    maxAgeInMonths = max(ageInMonths, na.rm = T),
  )

pe_gender <- pe %>% 
  group_by(ageInYears) %>%
  filter(gender == "f") %>% 
  summarise(
    nFemales = length(unique(subjID))
  )

pe_sample <- pe_sample %>% 
  left_join(pe_gender, by = c("ageInYears"))
```

## Participants
Our third aim was to assess whether the captured individual variation in gaze cue understanding relates to factors in children's real live social surroundings. For this exploratory analysis, we included all children of the aforementioned samples where families filled out a short demographic questionnaire. Our sample consisted of 
`r sum(pe_sample$nTotal)` children, including 
`r sum(pe_sample$nTotal[pe_sample$ageInYears == "3"])` 3-year-olds 
(mean = `r sum(pe_sample$meanAgeInMonths[pe_sample$ageInYears == "3"])` months, 
SD = `r sum(pe_sample$sdAgeInMonths[pe_sample$ageInYears == "3"])`, 
range = `r sum(pe_sample$minAgeInMonths[pe_sample$ageInYears == "3"])`
- `r sum(pe_sample$maxAgeInMonths[pe_sample$ageInYears == "3"])`, 
`r sum(pe_sample$nFemales[pe_sample$ageInYears == "3"])` girls),
`r sum(pe_sample$nTotal[pe_sample$ageInYears == "4"])` 4-year-olds 
(mean = `r sum(pe_sample$meanAgeInMonths[pe_sample$ageInYears == "4"])` months, 
SD = `r sum(pe_sample$sdAgeInMonths[pe_sample$ageInYears == "4"])`, 
range = `r sum(pe_sample$minAgeInMonths[pe_sample$ageInYears == "4"])`
- `r sum(pe_sample$maxAgeInMonths[pe_sample$ageInYears == "4"])`, 
`r sum(pe_sample$nFemales[pe_sample$ageInYears == "4"])` girls),
and `r sum(pe_sample$nTotal[pe_sample$ageInYears == "5"])` 5-year-olds 
(mean = `r sum(pe_sample$meanAgeInMonths[pe_sample$ageInYears == "5"])` months, 
SD = `r sum(pe_sample$sdAgeInMonths[pe_sample$ageInYears == "5"])`, 
range = `r sum(pe_sample$minAgeInMonths[pe_sample$ageInYears == "5"])`
- `r sum(pe_sample$maxAgeInMonths[pe_sample$ageInYears == "5"])`, 
`r sum(pe_sample$nFemales[pe_sample$ageInYears == "5"])` girls).

## Results
- peer exposure (hedge & box combined?)

@@

50 adults participated in the study. One additional subject returned their submission, i.e., decided to leave the study early or withdrew their submission after study completion. Data collection took place in May 2021. 
Participants were compensated with £1.25 for completing the study. We estimated an average completion time of 6 minutes, resulting in an estimated hourly rate of £10.00. In average, participants took 05:56min to complete the study. 
Participants were required to complete the study on a tablet or desktop. Participation on mobile devices was disabled since the display would be too small and would harm click precision. It was indicated that the study required audio sound.

@@

### Study 2 - Validation box version
As in study 1, we recruited participants on *Prolific*, and employed the same methodology. However, this time we focussed on validating the box version of the task in an adult sample. Participants were presented with eight boxes in which the target could land.
50 adults participated in the study. One additional subject returned their submission, i.e., decided to leave the study early or withdrew their submission after study completion. Data collection took place in June 2021. 
Participants were compensated with £1.00 for completing the study. We estimated an average completion time of 6 minutes, resulting in an estimated hourly rate of £10.00. In average, participants took 04:43min to complete the study.

@@

## Child sample
### Study 1 - Validation Remote and in-person
The validation of our task in a in-person and remote child sample can be found here: https://osf.io/snju6. 
We chose to have at least 20 data points per cell (i.e. unique combination of data collection mode, study version, and age-group). Across the two data collection modes, a total of ... children participated. Participants received a small gift as thank you for their participation in the study.

@@
